---
title: "Assignment 10 - 23Nov18"
author: "Charlene Thomas"
date: "11/22/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Assignment 10 - Lab

1. Write a function that calculates cumulative distribution function of a binomial random variable.

Compare results from your function with pbinom() function.

```{r}
p_binom <- function(x,size, probz) {
    total = sum(dbinom(0:x,size, probz))
  return(total)
}


p_binom(60, 100, 0.5)
pbinom(60,100,0.5)

library(microbenchmark)
microbenchmark(p_binom(60, 100, 0.5),pbinom(60,100,0.5))

```

2. Write a function that runs simulations to obtain power from a one-sample t-test. Run your function (with number of simulations = 10,000 ) with n = 30, delta = 0.5, sd = 1 and sig.level = 0.05. Compare your results with power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = ‘one.sample’).


```{r}
#Create Function
power_sim <- function(reps, n, mu0, delta, sigma, alpha) {
power <- replicate(reps,
                   {
x <- rnorm(n, mean = delta, sd = sigma)
tt <- as.numeric(t.test(x)$p.value < alpha)

}
)
return(sum(power)/length(power))
}

power_sim(10000, 30, 0, 0.5, 1, 0.05)

#Power.T.Test
power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = "one.sample")

microbenchmark(power_sim(10000, 30, 0, 0.5, 1, 0.05),power.t.test(n = 30, delta = 0.5, sd = 1, sig.level = 0.05, type = "one.sample"))

```
